Python as a machine learning language: experiences from the \textit{scikit-learn} project

### 2013-06-09 paper.tex
typo
Cosmit.

Started in 2009, \textit{scikit-learn} is developed by a large and
international team of volunteers, mostly researchers from
various fields (e.g., machine learning, natural language processing, or
neuroscience). The project also greatly benefits from many occasional
contributors proposing small code or documentation fixes or improvements.
Because of this large base of developers, emphasis is put on keeping
the project maintainable. In particular, code must follow specific
quality guidelines, such as style consistency, unit-test coverage. In
addition, complete documentation and examples are required for all
features. Finally, any addition to the code base goes through thorough
code review.

@@

A \texttt{FeatureUnion} object is a transformer combining multiple transformers
into a single one that joins their outputs. From an API point of view, a
\texttt{FeatureUnion} takes as input a list of transformers. Calling
\texttt{fit} on the union is the same as calling \texttt{fit} independently on
each of the transformers. For transforming data, the base transformers are
applied in parallel are their outputs are concatenated end-to-end into a larger
output.

>>>>

Started in 2009, \textit{scikit-learn} is developed by a large and
international team of volunteers, mostly researchers from
various fields (e.g., machine learning, natural language processing, or
neuroscience). The project also greatly benefits from many occasional
contributors proposing small code or documentation fixes or improvements.
Because of this large base of developers, emphasis is put on keeping
the project maintainable. In particular, code must follow specific
quality guidelines, such as style consistency and unit-test coverage. In
addition, complete documentation and examples are required for all
features. Finally, any addition to the code base goes through thorough
code review.

@@

A \texttt{FeatureUnion} object is a transformer combining multiple transformers
into a single one that joins their outputs. From an API point of view, a
\texttt{FeatureUnion} takes as input a list of transformers. Calling
\texttt{fit} on the union is the same as calling \texttt{fit} independently on
each of the transformers. For transforming data, the base transformers are
applied in parallel and their outputs are concatenated end-to-end into a larger
output.
